Computing the bicharacter of huge subspaces of polynomials

### 2019-07-05 article/article.tex
TODO notes

@@

	The grading can be refined into a multigrading by rows. The multigrading is preserved by the action of $\Sn$. The multigrading is not preserved by the action of $\GLr$, but instead carries exactly the information about the $\GLr$-character. It is thus equivalent to consider the $\GLr \times \Sn$-bicharacter or the $\Sn$ multigraded character of $R_{\Sn}$.

@@

	Therorem \ref{DiagHarm} has been proven for two sets of variables (see for example \cite{Bergeron2009}). It is not proven yet for more than two sets of variables but it has been verified by computation by Mike Zabrocki for a large number of sets of variables so we assume it to be true (since we will never reach that number of sets in our case).  \\

	The diagonal harmonics $\harmonics_n^{(r)}$ have been studied a lot until now. The character in the case $r=2$ is due to Garsia and Haiman (see \cite{GarsiaHaiman1993}) and some progress in the case $r=3$ had recently been made by Bergeron and Préville-Ratelle (see \cite{BergeronPreville2012}), but the general case is still unknown. Therefore, the computation of those characters should lead to a better understanding of those spaces.

	\subsection{Generalizations}

	In their article \cite{GarsiaHaiman1993}, Garsia and Haiman also introduced a generalized version of the Vandermonde determinant and a generalization of the diagonal harmonics for two sets of variables called the Gasia-Haiman modules.

>>>>

\nicolas{Ajouter des exemples au fur et à mesure}
\nicolas{figure de la matrice avec les actions de $\Sn$ et $\GLr$}

@@

	The natural grading of $R$ can be refined into a multigrading by rows. The multigrading is preserved by the action of $\Sn$. The multigrading is not preserved by the action of $\GLr$, but instead carries exactly the information about the $\GLr$-character. It is thus equivalent to consider the $\GLr \times \Sn$-bicharacter or the $\Sn$ multigraded character of $R_{\Sn}$.

@@

	Theorem \ref{DiagHarm} has been proven for two sets of variables (see for example \cite{Bergeron2009}). It is not proven yet for more than two sets of variables but it has been verified by computation by Mike Zabrocki for a large number of sets of variables so we assume it to be true (since we will never reach that number of sets in our case).  \\
        \nicolas{state conjecture explicitly + comment that we assume
          that it holds}

	\nicolas{fuse this paragraph with the earlier context about coinvariants}
	The diagonal harmonics $\harmonics_n^{(r)}$ have been studied a lot until now. The character in the case $r=2$ is due to Garsia and Haiman (see \cite{GarsiaHaiman1993}) and some progress in the case $r=3$ had recently been made by Bergeron and Préville-Ratelle (see \cite{BergeronPreville2012}), but the general case is still unknown. Therefore, the computation of those characters should lead to a better understanding of those spaces.

	\subsection{Generalizations}
	\nicolas{move to a later section, with 2-3 paragraphs of
          announcement in the introduction}
	In their article \cite{GarsiaHaiman1993}, Garsia and Haiman also introduced a generalized version of the Vandermonde determinant and a generalization of the diagonal harmonics for two sets of variables called the Gasia-Haiman modules.
